---
title: "Linear Regression"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Linear Regression}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(lab4package)
```

# Description
This linear regression package contains a reference class
which computes the coefficients, residuals, predicted values,
standard errors for both the coefficients and the residuals,
t-values and p-values, and the degrees of freedom of a model
matrix based on a provided formula and data set.

## Reference Class
The reference class is called "linreg". It can be created by supplying a formula and a data set like so:
```{r}
data("iris")

linreg_mod = linreg$new(Petal.Length~Sepal.Width+Sepal.Length, iris)
```
After the class has been created, several functions can be called.

### Functions
#### coef()
The coef() function returns a named vector of coefficients.
```{r}
data("iris")
linreg_mod <- linreg$new(Petal.Length~Sepal.Width+Sepal.Length, iris)
linreg_mod$coef()
```

#### pred()
The pred() function returns the predicted values.
```{r}
data("iris")
linreg_mod = linreg$new(Petal.Length~Sepal.Width+Sepal.Length, iris)
linreg_mod$pred()
```

#### resid()
The resid() function returns the predicted values.
```{r}
data("iris")
linreg_mod = linreg$new(Petal.Length~Sepal.Width+Sepal.Length, iris)
linreg_mod$resid()
```

#### print()
The print() function shows how the function was called and also prints the coefficients.
```{r}
data("iris")
linreg_mod = linreg$new(Petal.Length~Sepal.Width+Sepal.Length, iris)
linreg_mod$print()
```

#### summary()
The summary() function shows a detailed overview of all the relevant variables.
```{r}
data("iris")
linreg_mod = linreg$new(Petal.Length~Sepal.Width+Sepal.Length, iris)
linreg_mod$summary()
```

#### plot()
The plot() function displays two graphs; the first graph shows the relationship between the residuals and the fitted values, and the second graph shows the scale-location.
```{r}
data("iris")
linreg_mod = linreg$new(Petal.Length~Sepal.Width+Sepal.Length, iris)
linreg_mod$plot()
```
